On Sample Size for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2023-05-25 Manuscript/manuscript.tex
5/25 Manuscript Update

Based on Figure~\ref{fig:mu}, 
Student's $t$ CIs appear to have the greatest coverage rates with respect 
to estimating $\mu$. In fact, for $\phi = -0.4$, Student's $t$ CIs over-cover $\mu$
for all sample sizes, whereas other CIs have coverage rates that
hover around the $95\%$ line at this level of $\phi$. For $\phi = -0.2$, 
Standard, Percentile, Centered, and $BC_a$ CIs cover $\mu$ at the nominal 
rate when $n \geq 400$. Student's $t$ CIs either recover or over-cover $\mu$
for $n \geq 100$. For $\phi = 0$, or when the 
sample is independently normally distributed, $n = 800$ seems to 
be enough to recover $\mu$ when using Standard, Percentile, Centered, or $BC_a$ 
CIs. Student's $t$ CIs cover $\mu$ at the nominal rate for $n \geq 100$
For $\phi = 0.2$, $n = 3200$ seems to be large enough when using
Standard, Student's $t$, or Centered CIs, but Percentile and $BC_a$ CIs undercover
$\mu$ for all sample sizes at this level of $\phi$.
For $\phi = 0.4$, the Student's $t$ is the only type of CI that is able to recover $\mu$
for a sample as large as $n = 3200$. The other CIs undercover $\mu$ for all sample 
sizes at this level of $\phi$. Unsurprisingly, a greater level of $\phi$ demands a 
larger $n$ to recover $\mu$ at the nominal rate.

Based on Figure~\ref{fig:sigma}, 
$BC_a$ CIs greatly undercover $\sigma_x$ for all sample sizes, although
there is no trend of coverage deterioration, indicating that there may eventually
be a sample size large enough for $\sigma_x$ to be covered at the nominal level.
For $\phi = -0.4$, Standard Normal and Student's $t$ CIs recover $\sigma$ when 
$n = 3200$, whereas as the other CIs undercover $\sigma$ for all sample sizes.
For $\phi  = -0.2$, all CIs except for $BC_a$ are able to cover $\sigma$ at the 
nominal rate for $n \geq 1600$, and Student's $t$ CIs cover $\sigma$ at the 
nominal rate when $n \geq 800$. When $\phi = 0$, $n \geq 1600$ seems to 
be large enough if Standard and Student's $t$ CIs are used. For $\phi = 0.2$, 
consistent coverage of $\sigma$ at the nominal level appears to only be true
for Student's $t$ CIs for $n \geq 1600$. For $\phi = 0.4$, the Student's $t$ CI is 
able to reach nominal coverage of $\sigma$ when $n = 1600$, although in 
our results, coverage appears to drop below the nominal rate for $n = 3200$, 
indicating that perhaps an even larger $n$ is needed to recover $\sigma$ at
this level of $\phi$.

Based on Figure~\ref{fig:phi}, 
Percentile and $BC_a$ CIs deteriorate clearly for any level of temporal correlation,
so they should not be used. The deterioration becomes more evident
as the absolute value of $\phi$ increases, regardless of whether $\phi$ is 
negative or positive. When $\phi = -0.4$, Standard and Centered CIs 
recover $\phi$ at the nominal rate for $n \geq 400$. At this $\phi$ level,
Student's $t$ CIs either recover or over-cover $\phi$ for $n \geq 100$. When
$\phi = -0.2$, Standard and Centered CIs recover $\phi$ at $n = 800$, whereas 
Student's $t$ CIs recover $\phi$ for $n \geq 100$. When
$\phi = 0$, Standard and Centered CIs recover $\phi$ at $n = 3200$, and 
$n = 800$ seems to be sufficient for Student's $t$ CIs. For $\phi = 0.2$, Standard
and Centered CIs cover $\phi$ at the nominal rate for $n \geq 800$, whereas 
Student's $t$ CIs can accomplish this at $n \geq 400$. For $\phi = 0.4$, $n \geq 
800$ is large enough for Standard and Centered CIs. Student's $t$ CIs either
recover or over-cover $\phi$ for all $n \geq 100$.

To summarize, the CI type chosen should be based on the target parameter. 
When estimating $\mu$, the Student's $t$ CI seems to have the highest coverage
overall, although that leads to over-coverage when $\phi$ is -0.4. For a
sample with no temporal dependence, the Student's $t$ CI cover $\mu$ perfectly
at the nominal rate even for small sample sizes. For positive $\phi$, a larger
sample size appears to be necessary regardless of the CI used. In the case
that $\phi$ is unknown and expected to be greater than $0$, $n = 3200$ may be
necessary for block bootstrap interval estimation of $\mu$. If $\phi$ is known,
a lesser sample size may be sufficient. When estimating $\sigma$,
$BC_a$ should not be used, and Student's $t$ again has the greatest coverage
rates. In the case that $\phi$ is unknown and expected to be greater than $0$,
$n > 3200$ may be necessary for block bootstrap interval estimation of
$\sigma$. Again, if $\phi$ is known, a lesser sample size may be enough.
When estimating $\phi$, Percentile and $BC_a$ CIs 
deteriorate in coverage, indicating they should not be used in this context. 
Increasing $n$ will not fix the performance of either of these intervals 
because the assumption that the coverage rate will approach the nominal level
as $n$ increases is invalid. Centered and Standard CIs managed to fix the
deterioration problem, and they perform similarly, but Student's $t$ covers
$\phi$ at the nominal rate for much smaller sample sizes. It seems that 
$n = 800$ is large enough to
recover $\phi$ when using the Student's $t$ method.

@@

Again, this analysis \eds{what?} \mc{addressed} relies on the assumption that
there is a size $n$ large enough for the method to work: that is, the method's
performance improves as $n$ increases. Out of the five types of intervals used
in this study, this assumption was found to hold true with respect to
estimating $\phi$ only for Standard, Student's $t$, and Centered CIs, whereas both
Percentile and $BC_a$ intervals exhibited coverage deterioration as $n$
increased. The Percentile CI's coverage deterioration can be attributed to
bias that is not corrected as $n$ increases. Specifically, as $n$ increases, 
the width of the CI decreases, but because the Percentile CI
underestimates $\phi$, the coverage decreases. The $BC_a$ CI does seem to correct the bias, but the acceleration factor seems to fail, as the width of the CI
seems to be inconsistent.

When using Student's $t$ centered intervals and $\phi$ is
unknown, the results of this study suggest that an $n$ of around $3200$ may be
necessary for common practice to estimate simpler parameters like $\mu$ 
or $\sigma_x$. If $\phi$ is already known, a lesser $n$ may be adequate
to
estimate these parameters. For lower absolute values of $\phi$, a smaller
$n$ is sufficient when estimating $\mu$ or $\sigma$. For negative
values of $\phi$, coverage of $\mu$ is higher in general. In fact, 
Student's $t$ seems to over-cover $\mu$ for $\phi = 0.4$, 
meaning that if $\phi$ is known to have a very negative value, another CI
should be used.
However, in real world applications, $\phi$ is
more commonly found to be positive, so Student's $t$ should still be used
if $\phi$ is unknown.
Lastly, to estimate $\phi$, an $n$ of around $800$ using the 
Student's $t$ method
 may be sufficient.
Further investigation may be necessary to see if there are other interval
corrections that fix the coverage deterioration problem for $\phi$.

>>>>

Based on Figure~\ref{fig:mu}, 
Student's $t$ CIs appear to have the greatest coverage rates with respect 
to estimating $\mu$. In fact, for $\phi = -0.4$, Student's $t$ CIs over-cover $\mu$
for all sample sizes, whereas other CIs have coverage rates that
hover around the $95\%$ line at this level of $\phi$. For $\phi \geq -0.2$,
$BC_a$ CIs undercover $\mu$ for all $n$ observed. For $\phi = -0.2$, 
Standard, Percentile, CBP, Centered, and $BC$ CIs seem to 
generally cover $\mu$ at the nominal 
rate when $n \geq 400$. Student's $t$ CIs either recover or over-cover $\mu$
for $n \geq 100$. For $\phi = 0$, or when the 
sample is independently normally distributed, $n = 1600$ seems to 
be enough to recover $\mu$ when using Standard, Percentile, CBP, Centered, or $BC$ 
CIs. Student's $t$ CIs cover $\mu$ at the nominal rate for $n \geq 100$ at 
$\phi = 0$.
For $\phi = 0.2$, $n > 3200$ seems to be necessary to recover $\mu$
at the nominal level when using
any of the CIs, although some CIs, such as Student's $t$, are much closer to the
$95\%$ line than others, most notably $BC_a$.
For $\phi = 0.4$, a much larger sample size appears to be necessary. Once again,
Student's $t$ CIs are the closest to $95\%$ coverage, and $BC_a$ CIs are the furthest.

Based on Figure~\ref{fig:sigma}, 
$BC_a$ CIs greatly undercover $\sigma_x$ for every combination of $n$ and 
$\phi$, observed, although
there is no trend of coverage deterioration, indicating that there may eventually
be a sample size large enough for $\sigma_x$ to be covered at the nominal level.
For $\phi = -0.4$, Standard Normal and Student's $t$ CIs recover $\sigma$ when 
$n = 1600$, but undercover $\sigma$ for $n = 3200$, indicating
that a larger $n$ is most likely necessary to consistently cover $\sigma$ at the 
nominal rate.
The other CI types undercover $\sigma$ for all sample sizes at $\phi = 0.4$.
For $\phi  = -0.2$, all CIs except for $BC_a$ are able to cover $\sigma$ at the 
nominal rate for $n \geq 3200$, and Student's $t$ CIs cover $\sigma$ at the 
nominal rate when $n \geq 400$. When $\phi = 0$, $n \geq 1600$ seems to 
be large enough if Standard CIs are used, and $n \geq 400$ is fine is
Student's $t$ CIs are used. $n \geq 3200$ appears necessary 
for other CIs. For $\phi = 0.2$, 
comfortable coverage of $\sigma$ at the nominal level appears to only be true
for Student's $t$ CIs for $n \geq 3200$, although Standard and CBP CIs. For $\phi = 0.4$, a much larger sample size appears to be necessary. Student's $t$ CIs are the closest to $95\%$ coverage, and $BC_a$ CIs are the furthest.

Based on Figure~\ref{fig:phi}, 
Percentile, CBP, $BC$, and $BC_a$ CIs deteriorate clearly for any level of temporal correlation,
so they should not be used. The deterioration becomes more evident
as the absolute value of $\phi$ increases, regardless of whether $\phi$ is 
negative or positive. When $\phi = -0.4$, Standard and Centered CIs 
recover $\phi$ at the nominal rate for $n \geq 400$. At this $\phi$ level,
Student's $t$ CIs either recover or over-cover $\phi$ for $n \geq 100$. When
$\phi = -0.2$, Standard and Centered CIs recover $\phi$ at $n = 800$ and 
$n = 1600$, 
although they undercover $\phi$ at $n = 3600$, indicating that 
perhaps a larger $n$ is needed if these CIs are uses. However,
Student's $t$ CIs cover $\phi$ at the nominal level for $n \geq 400$. When
$\phi = 0$, Standard and Centered CIs recover $\phi$ relatively comfortably 
at $n = 3200$, and 
$n = 800$ seems to be sufficient for Student's $t$ CIs. For $\phi = 0.2$, Standard
and Centered CIs cover $\phi$ at the nominal rate for $n \geq 1600$, whereas 
Student's $t$ CIs can accomplish this at $n \geq 100$. For $\phi = 0.4$, $n \geq 
800$ is large enough for Standard and Centered CIs. Student's $t$ CIs either
recover or over-cover $\phi$ for all $n \geq 100$.

To summarize, the CI type chosen should be based on the target parameter. 
When estimating $\mu$, the Student's $t$ CI seems to have the highest coverage
overall, although that leads to over-coverage when $\phi$ is -0.4. For a
sample with no temporal dependence, the Student's $t$ CI cover $\mu$ perfectly
at the nominal rate even for small sample sizes. For positive $\phi$, a larger
sample size appears to be necessary regardless of the CI used. In the case
that $\phi$ is unknown and expected to be greater than $0$, $n > 3200$ may be
necessary for block bootstrap interval estimation of $\mu$. If $\phi$ is known,
a lesser sample size may be sufficient. When estimating $\sigma$,
$BC_a$ should not be used, and Student's $t$ again has the greatest coverage
rates. In the case that $\phi$ is unknown and expected to be greater than $0$,
$n > 3200$ may be necessary for block bootstrap interval estimation of
$\sigma$. Again, if $\phi$ is known, a lesser sample size may be enough.
When estimating $\phi$, Percentile and $BC_a$ CIs 
deteriorate in coverage, indicating they should not be used in this context. 
Increasing $n$ will not fix the performance of either of these intervals 
because the assumption that the coverage rate will approach the nominal level
as $n$ increases is invalid. Centered and Standard CIs managed to fix the
deterioration problem, and they perform similarly, but Student's $t$ covers
$\phi$ at the nominal rate for much smaller sample sizes. It seems that 
$n = 800$ is large enough to
recover $\phi$ when using the Student's $t$ method.

@@

Again, this analysis \eds{what?} \mc{addressed} relies on the assumption that
there is a size $n$ large enough for the method to work: that is, the method's
performance improves as $n$ increases. Out of the five types of intervals used
in this study, this assumption was found to hold true with respect to
estimating $\phi$ only for Standard, Student's $t$, and Centered CIs, whereas 
Percentile, CBP, $BC$, and $BC_a$ intervals exhibited coverage deterioration as $n$
increased. The Percentile CI's coverage deterioration can be attributed to
bias that is not corrected as $n$ increases. Specifically, as $n$ increases, 
the width of the CI decreases, but because the Percentile CI
underestimates $\phi$, the coverage decreases. The $BC_a$ CI does seem to correct the bias, but the acceleration factor seems to fail, as the width of the CI
seems to be inconsistent.

When using Student's $t$ centered intervals and $\phi$ is
unknown, the results of this study suggest that an $n > 3200$ may be
necessary for common practice to estimate simpler parameters like $\mu$ 
or $\sigma_x$. If $\phi$ is already known, a lesser $n$ may be adequate
to
estimate these parameters. For lower absolute values of $\phi$, a smaller
$n$ is sufficient when estimating $\mu$ or $\sigma$. For negative
values of $\phi$, coverage of $\mu$ is higher in general. In fact, 
Student's $t$ seems to over-cover $\mu$ for $\phi = 0.4$, 
meaning that if $\phi$ is known to have a very negative value, another CI
should be used.
However, in real world applications, $\phi$ is
more commonly found to be positive, so Student's $t$ should still be used
if $\phi$ is unknown.
Lastly, to estimate $\phi$, an $n$ of around $800$ using the 
Student's $t$ method
 may be sufficient.
Further investigation may be necessary to see if there are other interval
corrections that fix the coverage deterioration problem for $\phi$.
